Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-22 ms.tex
blah

\begin{figure}
\includegraphics[width=\columnwidth]{eta.pdf}
\caption{\label{fig:eta} Parameter $\eta$ characterizing stellar mass
  loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star formation histories from
  \citet{MosterNaab+:2013a}  Note that the star
  formation histories in \citet{MosterNaab+:2013a} are in terms of
  halo mass and for each $\Mbh$ we assign the halo mass,
  whose star formation history would produce a bulge consistent with
  the $\Mbh-M_{\rm bulge}$ relationship from
  \citet{McConnellMa:2013a}.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{rs_rIa.pdf}
\caption{\label{fig:rs_rIa} $\rIa/\rs$ vs. $\Mbh$. $\rIa$ is
  calculated using equation~\eqref{eq:rIa} {\bf AG: I am just
    referring to the first part of the equation here--I use the
    appropriate convolution the Ia rate here}. $\rs$ is calculated
  using the equation~\eqref{eq:stag_simple} and the $\vwO$
  corresponding to each $\Mbh$--see Figure~\ref{fig:vwSources}. For
  the blue curve we use the total $\vwO$ from stars, MSP, and
  black hole feedback (e.g. the solid black curve in
  Figure~\ref{fig:vwSources}).}
\end{figure}

@@

Figure~\ref{fig:miller} shows our predicted ${\rm L_{X}/L_{edd}}$ for
core (blue) and cusp (green) galaxies superimposed with x-ray
measurements (red stars), upper limits (red triangles) from
\citet{Miller+15}.  For our theoretical predictions $L_X=\epsilon
\Mdot c^2$, where $\epsilon$ is and efficiency factor and $\Mdot$ is
calculated using Equation~\eqref{eq:mdot_analytic}, with the value of
the wind heating parameter, $\vw$, and the mass return parameter,
$\eta$ set by the average star formation history for each $\Mbh$ (see
the black lines in Figures~\ref{fig:vwSources} and~\ref{fig:eta}). We
try two different prescriptions for $\epsilon$: 
$\epsilon=10^{-4}$ in the left-hand panel and $\epsilon=10^{-1}
\Mdot/0.01 \MdotEdd$ right-hand panel.

@@

% \begin{figure}
% \includegraphics[width=\columnwidth]{bh_xray.eps}
% \caption{\label{fig:bh_xray} X-ray luminosity plotted as a function of
%   stellar mass for our solutions (points), the trend of nuclear x-ray
%   luminosity with stellar mass (black line) and the detection upper
%   limit (blue line) from Fig. 1 of \citealt{Miller+15}. In
%   the top panel we take the X-ray luminosity to be $\epsilon_1 \Mdot
%   c^2$, with $\epsilon_1=5\times 10^{-7}$ chosen to make our
%   luminosities comparable to those observed. In the bottom panel, we
%   take the accretion power to be quadratic in $\Mdot$. $L_x=\epsilon_2
%   \eddr \Mdot c^2$ with $\epsilon2$=$2\times10^{-4}$. For each galaxy
%   we choose the $\vwO=200$ km/s solution.  {\bf BDM: if possible, add actual x-ray data from Gallo+08!}}
% \end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{eta.pdf}
\caption{\label{fig:eta} Parameter $\eta$ characterizing stellar mass
  loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star formation histories from
  \citet{MosterNaab+:2013a} (see appendix~\ref{app:windheat} for details).}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{rs_rIa.pdf}
\caption{\label{fig:rs_rIa} $\rIa/\rs$ vs. $\Mbh$. $\rIa$ is
  calculated using equation~\eqref{eq:rIa} {\bf AG: I am just
    referring to the first part of the equation here--I use the
    appropriate convolution the Ia rate here}. $\rs$ is calculated
  using the equation~\eqref{eq:stag_simple} and the $\vwO$
  corresponding to each $\Mbh$--see the black line
  Figure~\ref{fig:vwSources}.}
\end{figure}

@@

This is shown Figure~\ref{fig:miller} shows our predicted ${\rm
  L_{X}/L_{\rm edd}=\epsilon_X \Mdot c^2}$ for core (blue) and cusp
  (green) galaxies superimposed with x-ray measurements (red stars),
  upper limits (red triangles) from \citet{Miller+15}. $\epsilon_X$ is
  an efficiency factor and $\Mdot$ is calculated using
  Equation~\eqref{eq:mdot_analytic}, with parameters consistent with
  the average star formation history for each $\Mbh$ (see the black
  lines in Figures~\ref{fig:vwSources} and~\ref{fig:eta}). Our
  predicted trend in  $L_{X}/L_{\rm edd}$ is steeper than the 
  trend found in \citet{Miller+14} (black line). Note that we try two 
  different prescriptions for $\epsilon_X$: $\epsilon_X=10^{-4}$ in
  the left-hand panel and $\epsilon_X=10^{-1} \Mdot/0.01 \MdotEdd$
  right-hand panel. In either case our predicted trend in $
  L_{X}/L_{\rm edd}$ is opposite the observationally inferred
  one. {\bf AG-Need a bit more discussion here.} We note that in the
  right hand panel the observed galaxies are below the upper limits
  from Ia supernovae and thermal instability and so may be accreting
  in a thermally stable state {\bf AG-but it does not mean that they
    actually are}.

@@
